disturbance chronologies

### 2017-06-05 analysis/analysis_disturbance_chronos.Rmd
updating

# sjL <- sj[, c("SJ0101","SJ0102","SJ0201","SJ0202","SJ0301","SJ0302","SJ0401","SJ0402","SJ0501","SJ0502",
#               "SJ0601","SJ0602","SJ0603","SJ0701","SJ0702","SJ0801","SJ0802","SJ0901","SJ0902","SJ0903",
#               "SJ1001","SJ1002","SJ1003")]
# sjH <- sj[, c("SJ1101","SJ1102","SJ1103","SJ1201","SJ1202","SJ1203","SJ1301","SJ1302","SJ1303","SJ1401",
#               "SJ1402","SJ1501","SJ1502","SJ1601","SJ1602","SJ1701","SJ1702","SJ1703","SJ1801","SJ1802",
#               "SJ1901","SJ1902","SJ2001","SJ2003","SJ2002")]
```

@@

@@

  aux_df <- df %>%
    group_by(year) %>% 
    summarise(ntrees = length(tree),
              gc_m = mean(gc_mean),
              gc_m_sd = sd(gc_mean),
              gc_m_se = sd(gc_mean) / sqrt(n()), 
              gc_md = mean(gc_median),
              gc_md_sd = sd(gc_median),
              gc_md_se = sd(gc_median) / sqrt(n())) %>%  
    mutate(site=paste(d))

@@

gc_todos %>% ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('Mean GC') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))

## Númber of trees 
GC_trees <- function(gcdf, treshold){

@@

  # Get n tree with GC positve upper treshold 
  n_pos <- gcdf %>% filter(gc_m > th) %>% group_by(year) %>% summarise(n_pos = length(ntrees))

  # Get n tree with GC negative lower treshold 
  n_neg <- gcdf %>% filter(gc_m < (-1*th)) %>% group_by(year) %>% summarise(n_neg = length(ntrees))

@@

treesth <- GC_trees(gcdf = gc_todos, treshold = 50)

>>>>

@@

* calcular chronologies con media y mediana. 
* ver [./analysis/analysis_disturbance_chronos.md](/analysis/analysis_disturbance_chronos.md))

@@

  aux_df <- df %>%
    group_by(year) %>% 
    summarise(ntrees = length(ntrees),
              gc_m = mean(gc_mean),
              gc_m_sd = sd(gc_mean),
              gc_m_se = sd(gc_mean) / sqrt(n()), 
              gc_md = mean(gc_median),
              gc_md_sd = sd(gc_median),
              gc_md_se = sd(gc_median) / sqrt(n())) %>%  
    mutate(site=paste(d))

@@

gc_todos %>% ggplot(aes(x=year, y=gc_m)) + 
  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('Mean GC') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))
```

## Númber of trees 
```{r}

computeGCtrees <- function(gcdf, treshold){

@@

  # Get n tree with GC positve upper treshold 
  n_pos <- gcdf %>% dplyr::filter(gc_mean > th) %>% group_by(year) %>% summarise(n_pos = length(ntrees))

  # Get n tree with GC negative lower treshold 
  n_neg <- gcdf %>% dplyr::filter(gc_mean < (-1*th)) %>% group_by(year) %>% summarise(n_neg = length(ntrees))

@@

gc_trees<- c()

  au <- df %>% computeGCtrees(treshold = 50) %>% data.frame() %>% mutate(site = paste(d))
  gc_trees <- rbind(gc_trees, au)
}

xx <- gc_trees %>% 
  mutate(per_negn = (per_neg)*(-1))

gc_trees %>% ggplot() +
  geom_bar(aes(x=year, y=per_pos), fill='blue', stat = "identity", position = "dodge") +
  geom_bar(aes(x=year, y=(-1)*per_neg), fill='blue',  stat = "identity", position = "dodge") + 
  facet_wrap(~site, nrow = 3) +
  theme_bw() + ylab('%trees GC > 50 %') +
  theme(panel.grid = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))

gc_trees %>% ggplot() + 
  geom_point(aes(x=year, y=per_pos), shape=17) + 
  geom_point(aes(x=year, y=per_neg), shape=6) +
  facet_wrap(~site, nrow = 3)

  geom_bar(stat='identity', fill='gray', colour='gray') + theme_bw() + 
  # geom_point() +
  geom_errorbar(aes(ymin = gc_m - gc_m_se, ymax = gc_m + gc_m_se), colour='gray') +
  facet_wrap(~site, nrow = 3, scales = 'free_y',
             labeller=as_labeller(c('gc_caH' = 'Canar High', 
                                 'gc_caL' = 'Canar Low',
                                 'gc_sj' = 'San Juan'))) +
  geom_hline(yintercept=c(25, -25), linetype=2, colour='blue') +
  geom_hline(yintercept=c(50, -50), linetype=2, colour='red') + 
  ylab('Mean GC') + 
  theme(panel.grid.minor = element_blank(), 
        strip.background = element_rect(colour='black', 
                                        fill='white'))

computeGCtrees
